Conservative Model Order Reduction for Fluid Flow

### 2018-07-17 sections/5.res.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Comparison Skew symmetric, divergence and advective form %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \centering
  \begin{subfigure}[]{0.47\linewidth}
  \begin{tikzpicture}[scale=0.58]
    \begin{axis}[ylabel=$E_K(t)$,
                 xlabel=$t$,
                 label style={font=\large},
                 legend pos=south west,
                 legend entries={Skew Symmetric form, Divergence form, Advective form},
                 legend style={font=\large},
                 width=1.4\linewidth, 
                 height=1\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 yticklabel style={/pgf/number format/.cd,fixed,precision=4},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis]
                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Incompressible_Euler/Energy_compare_formulations/energy_skew_symmetric.txt};
                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Incompressible_Euler/Energy_compare_formulations/energy_divergence.txt};
                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Incompressible_Euler/Energy_compare_formulations/energy_convective.txt};
    \end{axis}%  
  \end{tikzpicture}
\caption{}
\label{compare_different_models}
\end{subfigure}
  \begin{subfigure}[]{0.47\linewidth}
\begin{tikzpicture}[scale=0.58]
    \begin{semilogyaxis}[ylabel = $\frac{\sigma_j}{\sum_i \sigma_i}$,
                 xlabel=Basis POD,
                 label style={font=\large},
                 %legend pos=north east,
                 %legend entries={$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis,
                 ymin=0,
                 ymax = 2,
                 samples = 100]
                 \addplot[color=black,style=solid,style=ultra thick]  table[x = x, y = s] {./data/Incompressible_Euler/Singular_values/sv.txt};
    \end{semilogyaxis}
\end{tikzpicture}
\caption{}
\label{singular_values_decay}
\end{subfigure}
  \caption{(\protect\subref{compare_different_models}) The kinetic energy $K$ for the advective, divergence and the skew-symmetric formulations. (\protect\subref{singular_values_decay}) The decay of the singular values for the vortex merging. }
  \label{fig:unstable_full_models}
\end{figure}
A total of $5000$ temporal snapshots is used to construct a reduced basis, following the process discussed in \Cref{sec:mor}. The decay of the singular values, used as an indication of the reducibility of the problem, is presented in \Cref{singular_values_decay}. The first $35$ POD modes corresponds to over $99\%$ of the modes of the high fidelity solution. This suggests that an accurate reduced system can be constructed using a small number of basis vectors. To illustrate the effectiveness of the method, smaller bases are also considered.

@@

\begin{figure}
  \centering
  \begin{subfigure}[]{0.48\linewidth}
  \begin{tikzpicture}[scale=0.55]
    \begin{semilogyaxis}[ylabel = $\left|\mathbf{1}^T(\mathbf{r}-\mathbf{r}^r)(t)\right|$,
                 xlabel=$t$,
                 label style={font=\large},
                 legend pos=north east,
                 legend entries={$k=200$ ,$k=300$, $k=400$,$k=500$,$k=600$},
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1.0\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis,
                 cycle list name=exotic]
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_200.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_300.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_400.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_500.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_600.txt};
    \end{semilogyaxis}%  
  \end{tikzpicture}
  \caption{}
  \label{mass_error_KH}
  \end{subfigure}\hfill
  \begin{subfigure}[]{0.48\linewidth}
  \begin{tikzpicture}[scale=0.55]
    \begin{semilogyaxis}[ylabel = $\left|(\mathbf{r}^{T}\mathbf{u}-\mathbf{r}^{rT}\mathbf{u}^{r})(t)\right|$,
                 xlabel=$t$,
                 label style={font=\large},
                 legend pos=north east,
%                 legend entries={$k=200$ Conv,$k=201$ Conv},
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1.0\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis,
                 cycle list name=exotic]
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_200.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_300.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_400.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_500.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_600.txt};
    \end{semilogyaxis}%  
  \end{tikzpicture}
  \caption{}
  \label{momentum_error_KH}
  \end{subfigure}

  \begin{subfigure}[]{0.48\linewidth}
  \begin{tikzpicture}[scale=0.55]
    \begin{semilogyaxis}[ylabel = $\left| \dfrac{1}{2}\left( \mathbf{u}^{rT}\mathbf{R}^r\mathbf{u}^r-\mathbf{u}^{T}\mathbf{R}\mathbf{u}\right)\right|$,
                 xlabel=$t$,
                 label style={font=\large},
                 legend pos=north east,
%                 legend entries={$k=200$ Conv,$k=201$ Conv},
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1.0\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis,
                 cycle list name=exotic]
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_200.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_300.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_400.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_500.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_600.txt};
    \end{semilogyaxis}%  
  \end{tikzpicture}
   \caption{}
  \label{energy_error_KH}
  \end{subfigure}
\caption{Difference between the high fidelity solution of the Kelvin-Helmholtz problem and the reduced solution of the mass (\protect\subref{mass_error_KH}), the momentum (\protect\subref{momentum_error_KH}), and the total energy (\protect\subref{energy_error_KH}).}
\label{fig:conservation_DEIM}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Comparison Skew symmetric, divergence and advective form %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \centering
  \begin{subfigure}[]{0.47\linewidth}
  \begin{tikzpicture}[scale=0.58]
    \begin{axis}[ylabel=$K$,
                 xlabel=$t$,
                 label style={font=\Large},
                 legend pos=south west,
                 legend entries={Skew Symmetric form, Divergence form, Advective form},
                 legend style={font=\large},
                 width=1.4\linewidth, 
                 height=1\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 yticklabel style={/pgf/number format/.cd,fixed,precision=4},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis]
                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Incompressible_Euler/Energy_compare_formulations/energy_skew_symmetric.txt};
                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Incompressible_Euler/Energy_compare_formulations/energy_divergence.txt};
                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Incompressible_Euler/Energy_compare_formulations/energy_convective.txt};
    \end{axis}%  
  \end{tikzpicture}
\caption{}
\label{compare_different_models}
\end{subfigure}
  \begin{subfigure}[]{0.47\linewidth}
\begin{tikzpicture}[scale=0.58]
    \begin{semilogyaxis}[ylabel = $\frac{\sigma_j}{\sum_i \sigma_i}$,
                 xlabel=Basis POD,
                 label style={font=\Large},
                 %legend pos=north east,
                 %legend entries={$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis,
                 ymin=0,
                 ymax = 2,
                 samples = 100]
                 \addplot[color=black,style=solid,style=ultra thick]  table[x = x, y = s] {./data/Incompressible_Euler/Singular_values/sv.txt};
    \end{semilogyaxis}
\end{tikzpicture}
\caption{}
\label{singular_values_decay}
\end{subfigure}
  \caption{(\protect\subref{compare_different_models}) The kinetic energy $K$ for the advective, divergence and the skew-symmetric formulations. (\protect\subref{singular_values_decay}) The decay of the singular values for the vortex merging. }
  \label{fig:unstable_full_models}
\end{figure}
A total of $5000$ temporal snapshots is used to construct a reduced basis, following the process discussed in \Cref{sec:mor}. The decay of the singular values, used as an indication of the reducibility of the problem, is presented in \Cref{singular_values_decay}. The first $35$ POD modes corresponds to over $99\%$ of the modes of the high fidelity solution. This suggests that an accurate reduced system can be constructed using a small number of basis vectors. To illustrate the effectiveness of the method, smaller bases are also considered.

@@

\begin{figure}
  \centering
  \begin{subfigure}[]{0.48\linewidth}
  \begin{tikzpicture}[scale=0.55]
    \begin{semilogyaxis}[ylabel = error in mass,
                 xlabel=$t$,
                 label style={font=\Large},
                 legend pos=north east,
                 legend entries={$k=200$ ,$k=300$, $k=400$,$k=500$,$k=600$},
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1.0\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis,
                 cycle list name=exotic]
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_200.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_300.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_400.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_500.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_600.txt};
    \end{semilogyaxis}%  
  \end{tikzpicture}
  \caption{}
  \label{mass_error_KH}
  \end{subfigure}\hfill
  \begin{subfigure}[]{0.48\linewidth}
  \begin{tikzpicture}[scale=0.55]
    \begin{semilogyaxis}[ylabel = error in total momentum,
                 xlabel=$t$,
                 label style={font=\Large},
                 legend pos=north east,
%                 legend entries={$k=200$ Conv,$k=201$ Conv},
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1.0\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis,
                 cycle list name=exotic]
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_200.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_300.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_400.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_500.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_600.txt};
    \end{semilogyaxis}%  
  \end{tikzpicture}
  \caption{}
  \label{momentum_error_KH}
  \end{subfigure}

  \begin{subfigure}[]{0.48\linewidth}
  \begin{tikzpicture}[scale=0.55]
    \begin{semilogyaxis}[ylabel = error in total energy,
                 xlabel=$t$,
                 label style={font=\Large},
                 legend pos=north east,
%                 legend entries={$k=200$ Conv,$k=201$ Conv},
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1.0\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis,
                 cycle list name=exotic]
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_200.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_300.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_400.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_500.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_600.txt};
    \end{semilogyaxis}%  
  \end{tikzpicture}
   \caption{}
  \label{energy_error_KH}
  \end{subfigure}
\caption{Difference between the high fidelity solution of the Kelvin-Helmholtz problem and the reduced solution of the mass (\protect\subref{mass_error_KH}), the momentum (\protect\subref{momentum_error_KH}), and the total energy (\protect\subref{energy_error_KH}).}
\label{fig:conservation_DEIM}
\end{figure}
